Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the normalization to vary later in the reconstruction process. We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation. As reference we chose the %observation with 
    \dvd{obsID} 1308. For \jolideco we use the GMM prior learned on the JWST Cas A image. As there are many counts in the image we additionally use an oversampling factor of 2. %For each observation 
    We allow the background level and position calibration to vary \dvd{among the observations}. As a reference for the positional shift we also use \dvd{obsID} %the observation with the ID 
    1308. Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly both improves the angular resolution and reduces the noise of the counts image.

@@

    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c } 
            \input{output/chandra-obs-table.tex}
        \end{tabular}
        \label{tab:chandra_obs}
        \script{chandra-obs-table.py}
        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}}
    \end{table}

>>>>

    We assume a spatially constant background of \qty[mode = text]{1e-5}{cts/pixel} but allow the normalization to vary later in the reconstruction process. We assume the exposure to be spatially constant and express its absolute value for each observation as the ratio of observation time with respect to a reference observation. As reference we chose the % 
    obsID 1308. For \jolideco we use the GMM prior learned on the JWST Cas A image. As there are many counts in the image we additionally use an oversampling factor of 2. We allow the background level and position calibration to vary among the observations. As a reference for the positional shift we also use \dvd{obsID} 1308. Figure~\ref{fig:example-chandra} shows the final result. \jolideco clearly both improves the angular resolution and reduces the noise of the counts image.

@@

    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c } 
            \input{output/chandra-obs-table.tex}
        \end{tabular}
        \label{tab:chandra_obs}
        \script{chandra-obs-table.py}
        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}}
    \end{table}
